---
title: "hw1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sessionInfo()
```

## 1. Average Waiting Time Between Eruptions

The average waiting time between eruptions of the *Old Faithful geyser* in the data set `faithful` is `r mean(faithful$waiting)` seconds.

## 2. First Four Eruption Durations

First four eruption durations of `faithful` dataset is as follows:
```{r}
faithful$eruptions[1:4]
```

## 3.First Five Records of the Eruptions Data

First 5 Rows of faithful dataset:

```{r, echo = FALSE, message = FALSE}
faithful_head <- head(faithful, n = 5)
kbl <- knitr::kable(faithful_head, format = "html")

if (!require(kableExtra)) {
  install.packages('kableExtra')
}
kableExtra::kable_styling(kbl, full_width = FALSE)
```

## 4. Histograms of Eruption Durations

```{r}
hist(faithful$eruptions,
     main = "Histogram of Eruption Durations",
     xlab = "Durations")
```

I expected a normal distribution, but the histogram is not normal. Eruption durations have two peaks: shorter than 2 seconds or between 4 to 5 seconds. *Old Faithful geyser* doesn't like the middle ground.

